### 2018-09-18 Manuscripts/cog-psych/revision/cogpsych.tex
Manuscript: fixed minor typo, cleaned a few sentences. This version sent as minor update to Ken and Nolan.

In the PACKER and copy-and-tweak models, the attention weights, $w$, specify the
importance of each dimension in the computation of similarity. While there exist
methods to find the optimal attention weighting scheme given a classification
\citep[see][]{vanpaemel2012using}, for simplicity we assume that the `Alpha' and
`Beta' categories are distinct along dimensions that the `Beta' exemplarss do
not vary on. In this case, the weighting for a given participant can be computed
as:

@@

The present work focuses on the influence of contrast on categorization,
primarily by exploring two different conceptualizations of contrast. However,
throughout this paper we have only explored one type of category generation
problem, that is the generation of new categories of squares that vary only in
size and shade. It is possible that the strength of the influence of contrast on
category generation decisions varies depending on the nature of the category
generation problem, for instance, in situations where the boundaries of the
domain are not clearly defined. To provide some intuition for this, consider the
following example: an entomologist is asked to draw a new type of insect that
they have never seen. Clearly, features of the new insect will be constrained by
the definition of an insect: it will be an arthropod with six legs and a
relatively hard exoskeleton. However, there are no strict limitations on other
features such as how large the insect needs to be, or if the insect should have
a particular type of pattern on its body. In this scenario, it is plausible that
the entomologist will draw an insect that is fairly similar to insects that
currently exist (e.g., small in size with a camouflage pattern that matches its
environment) as opposed to something completely different (e.g., a horse-sized
beetle with roman numerals on its back), indicating that contrast plays only a
minor role in the decision making process. In this situation it appears that
there is a combination of clearly defined constraints on the domain boundary
that are imposed by the external environment (insects must be arthropods with
six legs) but also ill-defined constraints that are imposed by the observer
(insects are probably small and have patterns on their body that suit the
environment). However, the relation of these contraints (and the interactions
between them) to the role of contrast is not currently well understood.

>>>>

In the PACKER and copy-and-tweak models, the attention weights, $w$, specify the
importance of each dimension in the computation of similarity. While there exist
methods to find the optimal attention weighting scheme given a classification
\citep[see][]{vanpaemel2012using}, for simplicity we assume that the `Alpha' and
`Beta' categories are distinct along dimensions that the `Beta' exemplars do
not vary on. In this case, the weighting for a given participant can be computed
as:

@@

The present work focuses on the influence of contrast on categorization,
primarily by exploring two different conceptualizations of contrast. However,
throughout this paper we have only explored one type of category generation
problem, that is the generation of new categories of new categories in an
artificial domain. It is possible that the strength of the influence of contrast on
category generation decisions varies depending on the nature of the category
generation problem, for instance, in situations where the boundaries of the
domain are not clearly defined. To provide some intuition for this, consider the
following example: an entomologist is asked to draw a new type of insect that
they have never seen. Clearly, features of the new insect will be constrained by
the definition of an insect: it will be an arthropod with six legs and a
relatively hard exoskeleton. However, there are no strict limitations on other
features such as how large the insect needs to be, or if the insect should have
a particular type of pattern on its body. In this scenario, it is plausible that
the entomologist will draw an insect that is fairly similar to insects that
currently exist (e.g., small in size with a camouflage pattern that matches its
environment) as opposed to something completely different (e.g., a horse-sized
beetle with roman numerals on its back), indicating that contrast plays only a
minor role in the decision making process. In this situation it appears that
there is a combination of clearly defined constraints on the domain boundary
that are imposed by the external environment (insects must be arthropods with
six legs) but also ill-defined constraints that are imposed by the observer
(insects are probably small and have patterns on their body that suit the
environment). However, the relation of these contraints (and the interactions
between them) to the role of contrast is not currently well understood.
